---
title: "Task1"
author: "Artem Slupskyi"
date: "27/10/2025"
format:
  html:
    embed-resources: true
editor: source
---

## Question 1 Atomic Types

Create the following variables related to your chosen object:

- **4 numeric** values (e.g., population, temperature, size, rating)  
- **3 integer** values (e.g., number of moons, buildings, inhabitants)  
- **2 logical** values (e.g., `has_water`, `is_inhabited`)  
- **3 character** values (e.g., `name`, `region`, `category`)

**Tip:** Think of these variables as *attributes* of your object.  
Use `print()` or `cat()` to describe them in one sentence.

```{r}
# code for solving task
population_density <- 6544.5 # people/sq. km

average_temperature <- 8.5       
area_km2 <- 182.0                
elevation_m <- 296.0             
tourism_rating <- 9.2            

# 3 integer values
population <- 720000            
districts <- 6                  
universities <- 12              

# 2 logical values
has_airport <- TRUE              
is_capital <- FALSE             

# 3 character values
city_name <- "Lviv"
region <- "Lviv Oblast"
category <- "Regional City"


```


## Question 2 Vectors

Create three different vectors:

1. **Numeric vector** combining all your numeric and integer variables.  
   *(Use `c()`.)*

2. **Sequence vector** from any number between 10–50 to 100, Choose step between 2 and 10.  
   *(Use `seq()` or `:`.)*

3. **Logical vector** of length 10 with random `TRUE`/`FALSE` values using `sample()`.


```{r}
# code for solving task
# 1. Numeric vector (combining numeric and integer variables)
numeric_vector <- c(8.5, 182.0, 296.0, 9.2, 720000, 6, 12)
print(numeric_vector)

# 2. Sequence vector (from 20 to 100, step = 5)
sequence_vector <- seq(from = 20, to = 100, by = 5)
print(sequence_vector)

# 3. Logical vector (length 10, random TRUE/FALSE values)
set.seed(123)  # for reproducibility
logical_vector <- sample(c(TRUE, FALSE), size = 10, replace = TRUE)
print(logical_vector)

```
## Question 3 Matrix

Create a **3×3 matrix** with random numbers between **-50 and 50**  
(using `sample()` or `runif()`), and name its **rows and columns** according to your theme.

Then calculate row and column averages using `rowMeans()` and `colMeans()`.

```{r}
# code for solving task
set.seed(42)
lviv_matrix <- matrix(sample(-50:50, 9, replace = TRUE), nrow = 3, ncol = 3)

rownames(lviv_matrix) <- c("Economy", "Culture", "Infrastructure")
colnames(lviv_matrix) <- c("2023", "2024", "2025")

row_avg <- rowMeans(lviv_matrix)
col_avg <- colMeans(lviv_matrix)

```

## Question 4 List  

Create a **list** that combines all your previous objects:  
atomic variables, vectors, and matrix.
Add one extra element — a short **description** of your universe as a string.

```{r}
# code for solving task
lviv_list <- list(
  # Atomic variables
  average_temperature = 8.5,
  area_km2 = 182.0,
  elevation_m = 296.0,
  tourism_rating = 9.2,
  population = 720000L,
  districts = 6,
  universities = 12,
  has_airport = TRUE,
  is_capital = FALSE,
  city_name = "Lviv",
  region = "Lviv Oblast",
  category = "Regional City",
  
  # Vectors
  numeric_vector = numeric_vector,
  sequence_vector = sequence_vector,
  logical_vector = logical_vector,
  
  # Matrix
  matrix = lviv_matrix,
  
  # Description
  description = "Lviv is a cultural and historical city in western Ukraine, known for its architecture and rich heritage."
)
```

## Question 5 Factor

Create a **factor variable** representing categories within your universe, e.g.:

- `"low"`, `"medium"`, `"high"`  
- `"infant"`, `"child"`, `"adult"`  
- `"poor"`, `"average"`, `"rich"`

Make sure you have **at least 5 observations** total.  
Then use `table()` to show how many objects fall into each category.

```{r}
# code for solving task
# Create a factor variable representing tourism levels in different districts of Lviv
tourism_level <- factor(
  c("high", "medium", "high", "low", "medium", "high"),
  levels = c("low", "medium", "high")
)

# Display frequency table
table(tourism_level)

```
## Question 6 Data Frame

Create a **data frame** related to your object that includes:

1. **5–8 observations** (rows)  
2. **At least 3 columns** of different data types  
   (e.g., name, numeric value, logical flag, category)

Then:

- Rename the columns using `names()` or `colnames()`.  
- Display its structure with `str()` and its summary with `summary()`.  
- Add a new column derived from the others (for example, a ratio or condition).

```{r}
# code for solving task
# Create a data frame related to the city of Lviv
lviv_data <- data.frame(
  district = c("Halytskyi", "Shevchenkivskyi", "Sykhivskyi", "Frankivskyi", "Lychakivskyi", "Zaliznychnyi"),
  population_thousands = c(150, 200, 180, 160, 120, 110),
  area_km2 = c(20.5, 25.3, 27.8, 22.4, 18.6, 16.7),
  has_university = c(TRUE, TRUE, FALSE, TRUE, FALSE, FALSE),
  tourism_level = factor(c("high", "medium", "medium", "high", "low", "low"),
                         levels = c("low", "medium", "high"))
)

# Rename columns
colnames(lviv_data) <- c("District", "Population_thousands", "Area_km2", "Has_university", "Tourism_level")

# Display structure and summary
str(lviv_data)
summary(lviv_data)

# Add a new column: population density (thousands per km²)
lviv_data$Density <- lviv_data$Population_thousands / lviv_data$Area_km2
```